%-------------------------------------------------------------------------------
% SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Projects}


%-------------------------------------------------------------------------------
% CONTENT
%-------------------------------------------------------------------------------
\begin{cventries}

%---------------------------------------------------------
  \cventry
    {University of Shiraz} % Place
    {Document Formatting Automation System} % Project Title
    {Shiraz, Iran} % Location
    {Mar 2023 - Sep 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Built a tool to check and correct document formatting based on university standards, automating compliance and reducing manual errors.}
        \item {\textbf{Technical Skills:} Python, Pandas, Regex, File Handling.}
        \item {\textbf{Soft Skills:} Problem-Solving, Attention to Detail, Logical Thinking.}
      \end{cvitems}
    }

    \cventry
    {University of Shiraz} % Place
    {Patients \& Hotel Management Systems} % Project Title
    {Shiraz, Iran} % Location
    {Jan 2023 - Apr 2023} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a management system for handling patient records and hotel reservations.}
        \item {\textbf{Technical Skills:} Flutter, SQL, API Integration, Database Design.}
        \item {\textbf{Soft Skills:} Teamwork, Project Management, Problem-Solving.}
      \end{cvitems}
    }

    \cventry
    {University of Shiraz} % Place
    {Local Twitter Clone} % Project Title
    {Shiraz, Iran} % Location
    {Jun 2022 - Sep 2022} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item {Developed a social media application with user authentication, real-time posting, and local database storage.}
        \item {\textbf{Technical Skills:} Flutter, SQLite, State Management, API Integration.}
        \item {\textbf{Soft Skills:} Teamwork, UI/UX Understanding, Debugging.}
      \end{cvitems}
    }

\end{cventries}
